A Parallel, Backjumping Subgraph Isomorphism Algorithm using Supplemental Graphs

### 2015-06-02 paper/paper.tex
Times include preprocessing
Include "no supplementals" curve

Our algorithm was implemented\footnote{source code is available at
\url{https://github.com/ciaranm/parasols}} in C++ using C++11 native threads, and was compiled using
GCC 4.9.0.  We performed our experiments on a machine with dual Intel Xeon E5-2640 v2 processors
(for a total of 16 cores, and 32 hardware threads via hyper-threading), running Scientific Linux
6.6.  For the comparison with SND in the following section, we used Java HotSpot 1.8.0\_11.

@@

In \cref{figure:cumulative} we show the cumulative performance of each algorithm. The value of
the line at a given time for an algorithm shows the total number of instances which, individually,
were solved in at most that amount of time. Our sequential implementation beats VF2 for times over
0.2s, LAD for times over 0.6s, and always beats SND. Our parallel implementation beats VF2 for times
over 0.06s, LAD for times over 0.02s, and always beats SND. Parallelism gives us an overall benefit
from 12ms onwards.

>>>>

Our algorithm was implemented\footnote{source code is available at
\url{https://github.com/ciaranm/parasols}} in C++ using C++11 native threads, and was compiled using
GCC 4.9.0.  We performed our experiments on a machine with dual Intel Xeon E5-2640 v2 processors
(for a total of 16 cores, and 32 hardware threads via hyper-threading), running Scientific Linux
6.6.  For the comparison with SND in the following section, we used Java HotSpot 1.8.0\_11. Runtimes
include preprocessing and thread launch costs, but not the time taken to read in the graph files
from disk (except in the case of SND, which we were unable to instrument).

@@

In \cref{figure:cumulative} we show the cumulative performance of each algorithm. The value of the
line at a given time for an algorithm shows the total number of instances which, individually, were
solved in at most that amount of time. Our sequential implementation beats VF2 for times over 0.2s,
LAD for times over 0.6s, and always beats SND.  Our parallel implementation beats VF2 for times over
0.06s, LAD for times over 0.02s, and always beats SND; parallelism gives us an overall benefit from
12ms onwards. Finally, removing supplemental graphs from our algorithm gives an improvement below 1s
(due to the cost of preprocessing), but is beneficial for longer runtimes.
